Inferring the Recombinant Genealogy of a Pandemic Pathogen in Real Time

### 2025-09-04 latex/main.tex

% This table is generated by the notebook tab_pango_x_events
\begin{table}
\caption{ARG events associated with Pango X lineages.
Each row corresponds to the oldest node assigned the specified
Pango lineage and the ancestor of all nodes assigned that label
(except XBB, XBB.1 and XM; see STAR methods). [MORE DETAILS]
\label{tab:pango_x_lineages}}
\begin{tabular}{lrrrrl}
\toprule
\multicolumn{5}{l}{Type I RE event: monophyletic for pango}\\
pango & averted & left & right & samples & nested \\
\midrule
XC & 37 & 26768 & 27390 & 5 & \{\} \\
XBR & 22 & 22034 & 22190 & 1 & \{\} \\
XA & 16 & 20411 & 21765 & 39 & \{\} \\
XS & 11 & 9054 & 10449 & 17 & \{\} \\
XL & 8 & 5925 & 8393 & 64 & \{\} \\
XBG & 8 & 22305 & 22917 & 25 & \{\} \\
XBD & 7 & 23020 & 24620 & 30 & \{\} \\
XQ & 7 & 4322 & 5386 & 55 & \{BA.2:37, $\star$\} \\
XBB & 6 & 22332 & 22577 & 6452 & \{BA.2:1\} \\
XM & 6 & 17411 & 21595 & 26 & \{BA.2:16, XAL:3\} \\
XBF & 5 & 5184 & 9866 & 185 & \{\} \\
XF & 5 & 5387 & 6402 & 16 & \{\} \\
XY & 5 & 11538 & 12880 & 23 & \{\} \\
XG & 4 & 5925 & 6513 & 3 & \{\} \\
XW & 4 & 2833 & 4321 & 32 & \{\} \\
\midrule
\multicolumn{5}{l}{Type II RE event}\\
alias & averted & left & right & total & by pango \\
\midrule
XAE+ & 6 & 24504 & 26060 & 253 & {BA.2:156, XZ:48, XAP:20, XAC:18, XAE:9, XAD:2} \\
XE/XH & 6 & 10448 & 11283 & 1156 & {XE:1116, BA.2:37, XH:2, XAF:1} \\
XBH & 6 & 15452 & 22001 & 6 & {BA.2:4, XBH:2} \\
XBM & 6 & 22305 & 22917 & 12 & {XBM:10, BF.3:2} \\
XAF & 5 & 10199 & 10447 & 36 & {BA.2:35, XAF:1} \\
XJ & 5 & 13196 & 17410 & 85 & {XJ:68, BA.2:17} \\
\bottomrule

\end{tabular}

>>>>

% This table is generated by the notebook tab_pango_x_events
\begin{table}
\caption{ARG events associated with Pango X lineages.
Each row corresponds to the oldest node assigned the specified
Pango lineage and the ancestor of all nodes assigned that label
(except XBB, XBB.1 and XM; see STAR methods). [MORE DETAILS]
\label{tab:pango_x_lineages}}
\begin{footnotesize}
\begin{tabular}{lrrrllrl}
\toprule
\multicolumn{5}{l}{Type I RE event: monophyletic for pango}\\
pango & avt & left & right & left p & right p & samp & nested \\
\midrule
XC & 37 & 26768 & 27390 & \textbf{AY.29} & \textbf{B.1.1.7} & 5 & {} \\
XBR & 22 & 22034 & 22190 & \textbf{BN.3.1} & BQ.1.25 & 1 & {} \\
XA & 16 & 20411 & 21765 & \textbf{B.1.177.18} & \textbf{B.1.1.7} & 39 & {} \\
XS & 11 & 9054 & 10449 & AY.103 & \textbf{BA.1.1} & 17 & {} \\
XL & 8 & 5925 & 8393 & \textbf{BA.1.17.2} & \textbf{BA.2} & 64 & {} \\
XBG & 8 & 22305 & 22917 & \textbf{BA.2.76} & \textbf{BA.5.2} & 25 & {} \\
XBD & 7 & 23020 & 24620 & \textbf{BA.2.75.2} & \textbf{BA.5.2.1} & 30 & {} \\
XQ & 7 & 4322 & 5386 & \textbf{BA.1.1.15} & \textbf{BA.2.9} & 55 & {BA.2:37,
XR:17, XAA:17, XU:1, XAM:21, XAG:6} \\
XBB & 6 & 22332 & 22577 & \textbf{BA.2.10} & BM.1.1.1 & 6452 & {BA.2:1} \\
XM & 6 & 17411 & 21595 & \textbf{BA.1.1} & \textbf{BA.2} & 26 & {BA.2:16,
XAL:3} \\
XBF & 5 & 5184 & 9866 & \textbf{BA.5.2.1} & CJ.1 & 185 & {} \\
XF & 5 & 5387 & 6402 & \textbf{AY.4} & \textbf{BA.1} & 16 & {} \\
XY & 5 & 11538 & 12880 & \textbf{BA.1.1} & \textbf{BA.2} & 23 & {} \\
XG & 4 & 5925 & 6513 & \textbf{BA.1.17} & \textbf{BA.2} & 3 & {} \\
XW & 4 & 2833 & 4321 & \textbf{BA.1.1.15} & \textbf{BA.2} & 32 & {} \\
\midrule
\multicolumn{5}{l}{Type II RE event}\\
alias & avt & left & right & left p & right p & desc & by pango \\
\midrule
XAE+ & 6 & 24504 & 26060 & \textbf{BA.2} & \textbf{BA.1.17.2} & 253 &
{BA.2:156, XZ:48, XAP:20, XAC:18, XAE:9, XAD:2} \\
XE/XH & 6 & 10448 & 11283 & \textbf{BA.1.17.2} & \textbf{BA.2} & 1156 &
{XE:1116, BA.2:37, XH:2, XAF:1} \\
XBH & 6 & 15452 & 22001 & \textbf{BA.2.1} & BA.2.75.2 & 6 & {BA.2:4, XBH:2} \\
XBM & 6 & 22305 & 22917 & \textbf{BA.2.76} & \textbf{BF.3} & 12 & {XBM:10,
BF.3:2} \\ XAF & 5 & 10199 & 10447 & \textbf{BA.1.1} & \textbf{BA.2} & 36 & {BA.2:35,
XAF:1} \\
XJ & 5 & 13196 & 17410 & \textbf{BA.1.17.2} & \textbf{BA.2} & 85 & {XJ:68,
BA.2:17} \\
\bottomrule
\multicolumn{5}{l}{Events closely derived from RE}\\
pango & alias & path len & time & mutations & samples \\
\midrule
XR & XQ & 3 & 11 & 4 & 17 \\
XU & XQ & 6 & 103 & 4 & 1 \\
XAM & XQ & 6 & 43 & 3 & 21 \\
XAA & XQ & 6 & 33 & 3 & 17 \\
XAG & XQ & 6 & 55 & 4 & 6 \\
XAP & XAE+ & 4 & 67 & 1 & 20 \\
XZ & XAE+ & 4 & 48 & 1 & 48 \\
XAE & XAE+ & 2 & 47 & 7 & 9 \\
XAF & XAF & 5 & 140 & 8 & 1 \\
XAL & XM & 3 & 66 & 2 & 3 \\
\midrule
\multicolumn{5}{l}{Non recombinant}\\
pango & muts & parent & samples & nested \\
\midrule
XP & 1 & \textbf{BA.1.1} & 45 & {} \\
XN & 1 & \textbf{BA.2} & 120 & {BA.2:1} \\
XBQ & 1 & CJ.1 & 14 & {} \\
XBK & 1 & CJ.1 & 7 & {} \\
XBE & 3 & BA.5.2 & 65 & {} \\
XB & 2 & B.1 & 192 & {} \\
XAZ & 3 & \textbf{BA.5} & 133 & {} \\
XAV & 3 & BA.5.1.24 & 13 & {} \\
XAU & 1 & BA.2 & 8 & {} \\
XAS & 1 & BA.4 & 77 & {} \\
XAN & 5 & \textbf{BA.5.1} & 7 & {} \\
XAJ & 11 & \textbf{BA.2.12} & 18 & {} \\
\bottomrule
\end{tabular}
\end{footnotesize}

% pango & averted & left & right & samples & nested \\

% \midrule
% XC & 37 & 26768 & 27390 & 5 & \{\} \\
% XBR & 22 & 22034 & 22190 & 1 & \{\} \\
% XA & 16 & 20411 & 21765 & 39 & \{\} \\
% XS & 11 & 9054 & 10449 & 17 & \{\} \\
% XL & 8 & 5925 & 8393 & 64 & \{\} \\
% XBG & 8 & 22305 & 22917 & 25 & \{\} \\
% XBD & 7 & 23020 & 24620 & 30 & \{\} \\
% XQ & 7 & 4322 & 5386 & 55 & \{BA.2:37, $\star$\} \\
% XBB & 6 & 22332 & 22577 & 6452 & \{BA.2:1\} \\
% XM & 6 & 17411 & 21595 & 26 & \{BA.2:16, XAL:3\} \\
% XBF & 5 & 5184 & 9866 & 185 & \{\} \\
% XF & 5 & 5387 & 6402 & 16 & \{\} \\
% XY & 5 & 11538 & 12880 & 23 & \{\} \\
% XG & 4 & 5925 & 6513 & 3 & \{\} \\
% XW & 4 & 2833 & 4321 & 32 & \{\} \\
% \midrule
% \multicolumn{5}{l}{Type II RE event}\\
% alias & averted & left & right & total & by pango \\
% \midrule
% XAE+ & 6 & 24504 & 26060 & 253 & {BA.2:156, XZ:48, XAP:20, XAC:18, XAE:9, XAD:2} \\
% XE/XH & 6 & 10448 & 11283 & 1156 & {XE:1116, BA.2:37, XH:2, XAF:1} \\
% XBH & 6 & 15452 & 22001 & 6 & {BA.2:4, XBH:2} \\
% XBM & 6 & 22305 & 22917 & 12 & {XBM:10, BF.3:2} \\
% XAF & 5 & 10199 & 10447 & 36 & {BA.2:35, XAF:1} \\
% XJ & 5 & 13196 & 17410 & 85 & {XJ:68, BA.2:17} \\
% \midrule
% \multicolumn{5}{l}{Nested monophyletic Pango X lineage}\\
% pango & alias & path len & time & mutations & samples & nested \\
% \midrule
% XAP & XAE+ & 4 & 67 & 1 & 20 & \{\} \\
% XZ & XAE+ & 4 & 48 & 1 & 48 & \{\} \\
% XAE & XAE+ & 2 & 47 & 7 & 9 & \{\} \\
% XAF & XAF & 5 & 140 & 8 & 1 & \{\} \\
% XAL & XM & 3 & 66 & 2 & 3 & \{\} \\
% XR & XQ & 3 & 11 & 4 & 17 & \{BA.2:1\} \\
% XU & XQ & 6 & 103 & 4 & 1 & \{\} \\
% XAM & XQ & 6 & 43 & 3 & 21 & \{\} \\
% XAA & XQ & 6 & 33 & 3 & 17 & \{\} \\
% XAG & XQ & 6 & 55 & 4 & 6 & \{\} \\

% \bottomrule
% \end{tabular}
